\begin{abstract}

This report presents the design and implementation of a complete \textbf{DevSecOps} platform
built around a modern web application developed with React, TypeScript and Vite, deployed on
\textbf{Google Kubernetes Engine (GKE)} in Autopilot mode. The project starts from an initial
situation where the team was using only \textbf{Jenkins} as a continuous integration pipeline
to run unit tests, with no integrated security considerations whatsoever.

The main objective is to transform this naive approach into a \textbf{secure end-to-end software
value chain}, integrating: Infrastructure as Code with Terraform, GitOps with Argo CD,
vulnerability analysis with Trivy and OWASP ZAP, runtime security with Wazuh SIEM, observability
with Prometheus and Grafana, and a keyless identity model via Workload Identity Federation.

The result is a reproducible, auditable platform directly applicable to real production contexts,
demonstrating that security does not hinder delivery velocity but rather enables confidence
in every deployment.

\vspace{0.5cm}
\keywordss{DevSecOps, Kubernetes, GKE, Terraform, Argo CD, Trivy, OWASP ZAP, Wazuh, CI/CD,
GitOps, Zero Trust, Workload Identity, SAST, DAST, SCA, GitHub Actions, Prometheus, Grafana.}

\vspace{1.5cm}
\centerline{\large\bf Résumé}
\vspace{0.6cm}

Ce rapport présente la conception et l'implémentation d'une plateforme \textbf{DevSecOps} complète
autour d'une application web moderne développée avec React, TypeScript et Vite, déployée sur
\textbf{Google Kubernetes Engine (GKE)} en mode Autopilot. Le projet part d'une situation initiale
où l'équipe utilisait uniquement \textbf{Jenkins} comme pipeline d'intégration continue pour
exécuter des tests unitaires, sans aucune considération de sécurité intégrée.

L'objectif principal est de transformer cette approche naïve en une \textbf{chaîne de valeur
logicielle sécurisée de bout en bout}, en intégrant~: l'Infrastructure as Code avec Terraform,
le GitOps avec Argo CD, l'analyse de vulnérabilités avec Trivy et OWASP ZAP, la sécurité runtime
avec Wazuh SIEM, l'observabilité avec Prometheus et Grafana, et un modèle d'identité sans clés
statiques via Workload Identity Federation.

Le résultat est une plateforme reproductible, auditable et directement applicable à des contextes
de production réels.

\vspace{0.5cm}
\keywords{DevSecOps, Kubernetes, GKE, Terraform, Argo CD, Trivy, OWASP ZAP, Wazuh, CI/CD,
GitOps, Zero Trust, Workload Identity, SAST, DAST, SCA, GitHub Actions, Prometheus, Grafana.}

\end{abstract}
