
%=== File containing Global Configuration of the report ===%
% Configure your cover pages and abstracts here            %
%==========================================================%

%============= Config new columns type ==============%
\newcolumntype{L}{>{\raggedright\arraybackslash}}
\newcolumntype{R}{>{\raggedleft\arraybackslash}}
\newcolumntype{C}{>{\centering\arraybackslash}}
%==================================================%

%========= Config the cover section ==========%

\title{Industrialisation DevSecOps d'une Application Web Cloud-Native}

\author{NAFFATI}

\diplomaName{Diplôme National d'Ingénieur}
\speciality{Génie Logiciel}

%% Encadrant professionnel
\proFramerName{Sopra HR Software}
\proFramerSpeciality{}

%% Encadrant académique
\academicFramerName{ESPRIT}
\academicFramerSpeciality{}

%% Entreprise d'accueil
\companyName{Sopra HR Software}

%% Année universitaire
\collegeYear{2025 - 2026}

%%%%%% Signatures section %%%%%%
\proSignSentence{J'autorise l'étudiant à faire le dépôt de son rapport de stage en vue d'une soutenance.}
\academicSignSentence{J'autorise l'étudiant à faire le dépôt de son rapport de stage en vue d'une soutenance.}

%%% FR
\frenchAbstract{Ce rapport présente la conception et l'implémentation d'une plateforme \textbf{DevSecOps} complète
autour d'une application web moderne développée avec React, TypeScript et Vite, déployée sur
\textbf{Google Kubernetes Engine (GKE)} en mode Autopilot. Le projet s'inscrit dans le cadre de
l'équipe QA de \textbf{Sopra HR Software}, qui utilisait jusqu'alors un framework BDD interne
(\textbf{T4T}) exécuté sur un serveur \textbf{Jenkins} basique, sans aucune considération de
sécurité intégrée.

La mission confiée est triple~: concevoir de nouveaux pipelines CI/CD modernes, intégrer la
sécurité à chaque étape (SAST, SCA, DAST), et produire des rapports d'analyse automatisés.
La solution intègre~: l'Infrastructure as Code avec Terraform, le GitOps avec Argo CD,
l'analyse de vulnérabilités avec Trivy et OWASP ZAP, la sécurité runtime avec Wazuh SIEM,
l'observabilité avec Prometheus et Grafana, et un modèle d'identité sans clés statiques via
Workload Identity Federation.

Le résultat est une plateforme reproductible, auditable et directement transposable aux projets
réels de l'équipe QA.
}

\frenchAbstractKeywords{DevSecOps, Kubernetes, GKE, Terraform, Argo CD, Trivy, OWASP ZAP, Wazuh, CI/CD,
GitOps, Zero Trust, Workload Identity, SAST, DAST, SCA, GitHub Actions, Prometheus, Grafana.}

%%% EN
\englishAbstract{This report presents the design and implementation of a complete \textbf{DevSecOps} platform
built around a modern web application developed with React, TypeScript and Vite, deployed on
\textbf{Google Kubernetes Engine (GKE)} in Autopilot mode. The project takes place within the
QA team of \textbf{Sopra HR Software}, which previously relied on an internal BDD testing
framework (\textbf{T4T}) executed on a basic \textbf{Jenkins} server, with no integrated
security considerations whatsoever.

The assigned mission is threefold: design modern CI/CD pipelines to replace the legacy Jenkins
approach, integrate security at every stage (SAST, SCA, DAST), and produce automated,
auditable analysis reports. The solution integrates: Infrastructure as Code with Terraform,
GitOps with Argo CD, vulnerability analysis with Trivy and OWASP ZAP, runtime security with
Wazuh SIEM, observability with Prometheus and Grafana, and a keyless identity model via
Workload Identity Federation.

The result is a reproducible, auditable platform directly transferable to the QA team's
real-world projects, demonstrating that security does not hinder delivery velocity but rather
enables confidence in every deployment.
}

\englishAbstractKeywords{DevSecOps, Kubernetes, GKE, Terraform, Argo CD, Trivy, OWASP ZAP, Wazuh, CI/CD,
GitOps, Zero Trust, Workload Identity, SAST, DAST, SCA, GitHub Actions, Prometheus, Grafana.}

